FTLR proof cases

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
Some trivial changes.

\paragraph{Case: $\protect\tjmp{\trg{r}}$}

\paragraph{Case: $\protect\tjnz{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tisptr{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tgeta{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgetb{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgete{\trg{r}}{\trg{r}}\mid$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tgetlin{\trg{r}}{\trg{r}}$}
Similar to the case for $\tisptr{\trg{r}}{\trg{r}}$.

\paragraph{Case: $\protect\tmove{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tstore{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tload{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tcca{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\trestrict{\trg{r}}{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tlt{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsetatob{\trg{r}}{\trg{r}}$}

@@

\paragraph{Case: $\protect\tcseal{\trg{r}}{\trg{r}}{\trg{r}}$}

\paragraph{Case: $\protect\tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsplice{\trg{r}}{\trg{r}}{\trg{r}}$}

>>>>

\paragraph{Case: $\protect\tjmp{\trg{r_1}}$}

\paragraph{Case: $\protect\tjnz{\trg{r_1}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tisptr{\trg{r_1}}{\trg{r_2}}$}

\paragraph{Case: $\protect\tgeta{\trg{r_1}}{\trg{r_2}}$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tgetb{\trg{r_1}}{\trg{r_2}}$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tgete{\trg{r_1}}{\trg{r_2}}\mid$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tgetlin{\trg{r_1}}{\trg{r_2}}$}
Similar to the case for $\tisptr{\trg{r_1}}{\trg{r_2}}$.

\paragraph{Case: $\protect\tmove{\trg{r_1}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tstore{\trg{r_1}}{\trg{r_2}}$}

\paragraph{Case: $\protect\tload{\trg{r_1}}{\trg{r_2}}$}

\paragraph{Case: $\protect\tcca{\trg{r_1}}{\trg{\rn}}$}

\paragraph{Case: $\protect\trestrict{\trg{r_1}}{\trg{r_2}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tlt{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tplus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tminus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsetatob{\trg{r_1}}{\trg{r_2}}$}

@@

\paragraph{Case: $\protect\tcseal{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$}

\paragraph{Case: $\protect\tsplit{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}{\trg{\rn}}$}

\paragraph{Case: $\protect\tsplice{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$}
